Boson-Sampling with Single Photons: A Roadmap to Post-Classical Computation

### 2016-10-15 roadmap.tex
penultimate

\begin{abstract}
Boson-sampling is thus far the most feasible approach for first demonstrating the supremacy of quantum computation over classical computation in the near future. We take the view that proof-of-principle demonstration of quantum supremacy is a pressing goal, with enormous implications, and should be considered an utmost priority by the experimental community. Here we strive to outline a roadmap to achieving this elusive goal, examining competing architectures and technologies, and paving the way forward for the first experimental demonstration of post-classical computation. We firstly develop a practical model to compare the performance of boson-samplers and classical simulators. In this model, we find that low-photon-number boson-sampling operating in the current experimental regime (\mbox{$n<10$} photons) could beat present commodity computers with GHz clock-rates only if the overall system efficiency and repetition rate are sufficiently high. Further, we calculate the required efficiency and photon-number to surpass classical computers of different clock-rates using various experimental schemes. Especially, we find that only if both photon-number-resolving detectors and high-speed optical shutters are available, scattershot boson-sampling is feasibly scalable to tens of photons. In order to provide a clear roadmap for boson-sampling, we also review and discuss various state-of-the-art technologies for single-photon sources, quantum circuits, and single-photon detectors.
\end{abstract}

@@

In Sec.~\ref{sec:sampling_time}, taking the repetition rate of the sampling system into account, we develop a rigorous and fair model for comparing the performance of boson-samplers and classical simulators. Given a certain classical computer, the regime of quantum supremacy of boson-sampling is specified by a simple continuous curve in the plane of total efficiencies versus photon-number. \comment{To our surprise, there is such a (optimal) turning point in this curve where four-photon boson-samplers with repetition rates of 76MHz could beat present commodity computers with GHz clock-rates}. Based upon this, such a computer could only be defeated by \mbox{$20\sim 30$}-photon boson-sampling \cite{bib:2, bib:3}. Furthermore, in Sec.~\ref{sec:exp_schemes}, we calculate the required efficiencies and photon-numbers for different experimental schemes to outperform classical computers of given clock-rates. In particular, we find that both photon-number-resolving detectors and high-speed optical shutters are indispensable to correctly implementing scattershot boson-sampling with tens of photons.

An intact boson-sampler includes three parts (see Fig.~\ref{fig:model}): single-photon sources, passive linear optical circuits, and single-photon detectors. A number of small-scale boson-sampling implementations have been reported in optical waveguides \cite{bib:4, bib:5, bib:6, bib:7, bib:8, bib:9} and fibre beamsplitters \cite{bib:10} using spontaneous parametric down-conversion (SPDC) sources, and fibre-loops \cite{bib:11} with quantum dot (QD) sources. In Sec.~\ref{sec:adv_sources}, we introduce some of the most promising single-photon sources and their recent advances, including SPDC, four-wave mixing (FWM) and QDs. In Sec.~\ref{sec:adv_networks}, we review and discuss some advances in linear optical networks, including optical waveguides, fibre-loops, and fibre beamsplitters. In Sec.~\ref{sec:adv_detectors}, we consider single-photon detectors (SPD), including single-photon avalanche photodiodes (SPAD), superconducting nanowire single-photon detectors (SNSPD) and transition-edge sensors (TES). These three types of detectors represent the most mature, high-speed, and near-unit efficiency respectively.

@@

How can a classical computer simulate this bosonic process, and sample from its exact or approximate probability distribution? A na{\"i}ve brute-force method is to calculate all $|\Phi|$ permanents of the set of submatrices $U_{S,T_i}$, thereby determining the full probability distribution, and then sample from this known distribution. \textbf{\comment{However, neither does the boson-sampler know even the approximate probability distribution before enough samples are obtained}} \comment{What does that sentence mean?}. Smarter classical algorithms exist to generate correct samples without knowing the entire underlying distribution. For example, using the acceptance-rejection method \cite{bib:15} \comment{Is there a better reference than Wikipedia?} one can sample an output configuration $\ket{T_i}$ uniformly from the configuration space and a number $u$ from the uniform distribution over $\{0,1\}$, then calculate the permanents of the respective submatrices and compare them to $u$; If \mbox{$u<|\mathrm{Per}(U_{S,T_i})|^2$}, we accept the sample $\ket{T_i}$; If not, it is rejected, and we repeat. Such methods could be successful with probability $O(1)$. One sample only requires calculating one permanent, significantly better than the brute-force method of calculating the entire distribution.

@@

As described above, the circuit itself consumes time resources $m^2\tau$, thus the effective repetition rate is,
\begin{align}
\frac{1}{m^2\tau}=\frac{R'}{m^2},
\end{align}
where $R'$ is the repetition frequency of the photonic time-bins, which we use instead of $R$ in Eq.~\ref{eq:tau_q} to obtain,
\begin{align}
\tau_t = \frac{m^2}{\eta^n R'}.
\end{align}
Comparing $\tau_t$ with $\tau_c$ and \comment{following the same way for original boson-sampling in Sec.~\ref{sec:sampling_time} \textbf{What does this mean?}}, we plot the critical photon-number to reach quantum supremacy as a function of $\eta$ for the time-bin encoding scheme.

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{curves_2}
\caption{The quantum and classical supremacy of (a) temporal-encoding, and (b) hybrid-encoding boson-sampling, is divided by the red line, where quantum supremacy is in the top-right region, and vice versa. The numbers 3, 6, etc. in the line refer to $10^3$FLOPS, $10^6$FLOPS etc. of classical computers respectively. The efficiency denoted on the horizontal axis is the overall system efficiency. Given the magnitude of the coupling strength, a single step including a beam splitter operation and phase-shifting operation takes \mbox{$\tau\sim0.3\mu\mathrm{s}$} \cite{bib:20}. Effective repeat frequency (a) \mbox{$R'=1/(13\mathrm{ns}\cdot 10^4)$}, (b) \mbox{$R'=1/(0.3\mu\mathrm{s}\cdot n^2).$} \comment{Why aren't the curves monotonic?! It's very strange that the curves change direction as photon-number increases??}} \label{fig:curves_2}
\end{figure}

@@

Compared to fabricating a unitary network in waveguides, the spatial degree of freedom in the transverse axis is retained as there are $m$ storage resonators and auxiliary qubits in microwave boson-sampling. But the longitudinal spatial modes are replaced by $m$ controlled temporal steps. Suppose a single step including a beamsplitter operation and phase-shift operation takes time $\tau_m$, so the total operational time for an \mbox{$m\times m$} unitary transformation is $\tau_m m$ \comment{Shouldn't this be $m^2$?}. Taking the reciprocal of the total operational time as the effective repeat frequency, we obtain the formula for $\tau_q$ for this scheme. Comparing with $\tau_c$, we plot the supremacy boundary for microwave boson-sampling, shown in Fig.~\ref{fig:curves_2}(b).

From the perspective of the encoding scheme, the sampling speed (unitary transformation) of the microwave boson-sampler is much slower than that of spatially-encoding boson-samplers. As shown in Fig.~\ref{fig:curves_2}, to beat the same advanced classical computer, we actually need higher system efficiency or a larger number of photons if the microwave scheme is utilised. However, the advantage of the superconducting platform exactly lies in its marvelously high fidelities ($>0.90$) of generation and measurement processes \cite{bib:21}, to which no ordinary optical boson-sampler is comparable. Though with high processing speed, the effective repeat frequency of a spatially-encoded optical boson-sampler is greatly reduced by post-selection due to the limited collection and detection efficiency. \comment{This doesn't make sense to me - explain it better}

@@

Recently, Aaronson and Brod \cite{bib:33} demonstrated that if $O(1)$ photons are lost at the input (i.e. $k$ out of \mbox{$n+k$}), the probability of each output configuration is given by,
\begin{align}
\mathrm{Pr}(T) = \frac{1}{|\Lambda_{n+k,n}|} \sum_{s\in m,n+k,n} |\mathrm{Per}(U_{S,T})|^2.
\end{align}
\comment{Need to define $\Lambda$ and meaning of $s\in m,n+k,n$.}

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{curves_loss}
\caption{The quantum and classical supremacy of boson-sampling with lost photons is separated by the red line, where the top-right side corresponds to the quantum regime and vice versa. Here the clock speed of the classical computer is gigaFLOPS, i.e $10^9$FLOPS. The efficiency denoted on the horizontal axis is the overall system efficiency. The numbers 0, 1, 2 \emph{etc.} in the line refer to the number of lost photons, $n_\mathrm{lost}$. The detection efficiency: (a) \mbox{$\eta_d=0.5$} (b) \mbox{$\eta_d=1$}. \comment{(Why does the curve have the change in direction?})} \label{fig:curve_hybrid}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.5\columnwidth]{curve_scattershot}
\caption{The quantum and classical supremacy of scattershot boson-sampling is separated by the red line, where the top-right region belongs to quantum supremacy and vice versa. The numbers 3, 6, etc. on the lines refer to $10^3$FLOPS, $10^6$FLOPS etc. of classical computers respectively. The efficiency denoted on the horizontal axis is the overall system efficiency \comment{(is that efficiency per mode, or total efficiency??)} except the preparation efficiency of the source, whereby the preparation efficiency of $n$ sources is substituted with $1/\sqrt{2\pi n}$ \cite{bib:36}.} \label{fig:curve_scattershot}
\end{figure}

@@

When the detectors are perfect but non-number-resolving, the probability that $n$ heralding detectors are triggered, and all of them result from single-photon pairs generated by $n$ SPDCs (ignoring higher order terms) is,
\begin{align}
p_\mathrm{input-correct} = \binom{m}{n} p^n(1-p-p^2)^{m-n}.
\end{align}
The total probability that $n$ SPDC sources generate photons is given by
\begin{align}
p_\mathrm{input-total} = \sum_{i=0}^n \binom{m}{n-i,i}p^{n+i}(1-p-p^2)^{m-n}.
\end{align}
\comment{What's the funny binomial?}. Nevertheless, we cannot distinguish the correct preparation of $n$ single photons from the total occasions of $n$ heralded sources. As shown in Fig.~\ref{fig:SBS_pair_gen}, the correct generation ratio, defined as $p_\mathrm{input-correct}/p_\mathrm{input-total}$, decreases rapidly with increasing $n$.

@@

In SPDC, a laser pumps a second-order nonlinear material (e.g. BBO or KDP) and creates two photons under the constraints of momentum and energy conservation (known as phase-matching). There are several different types of phase matching:
\begin{itemize}
\item Type-I: Both photons have the same polarisation.
\item Type-II: Both photons have orthogonal polarisation.
\item Type-0: All polarisations are identical. \comment{How is this different to type-I?}
\end{itemize}
Additionally, so-called quasi-phase-matching in a periodically-poled structure allows a positive net flow of down-conversion, and collinear propagation direction, thus eliminating spatial walk-off effects in the transverse direction \comment{Maybe we could explain what this means? I'm a theorist and I don't know these terms :)}. As a result, the best collection efficiency of \mbox{$\sim 90\%$} is realised with quasi-phase-matching \cite{bib:41, bib:42}.

@@

The problem of physical size \comment{I don't understand this sentence???} also haunts another popular platform in the field of optical quantum information processing -- fused silica waveguides, fabricated using femtosecond laser direct-written (FLDW) technology. Unlike PLC fabrication, the FLDW is a powerful and flexible technique for rapid 3D fabrication, requiring no masking procedure or cleanroom environment. However, this one-step fabrication process also makes the propagation loss rely heavily on the motion control accuracy of the precision stage \cite{bib:63}. FLDW waveguides exhibit lowest losses on the order of 0.1dB/cm \cite{bib:63}, substantially higher than that of PLC waveguides. Also, the maximum refractive index contrast achieved so far is 1\%, which limits waveguide bends to a radius of about 15mm (see Tab.~\ref{tab:one}).

@@

\section{A vision for the future -- the post-classical era}

@@

In our model, we can easily determine how many single-photons, and what repeat frequency and efficiency are needed to beat classical computers with given clock-speeds. To attain quantum supremacy, there are lower single-photon number thresholds ($<20$ photons) in systems with higher efficiencies and repeat frequencies. Therefore, improving repeat frequency plays a bigger role than photon number for those circuits with limited size but high transmittance, e.g., bulk optical circuits. \comment{Don't quite understand this last sentence}.

>>>>

\begin{abstract}
Boson-sampling is thus far the most feasible approach for first demonstrating the supremacy of quantum computation over classical computation in the near future. We take the view that proof-of-principle demonstration of quantum supremacy is a pressing goal, with enormous implications, and should be considered an utmost priority by the experimental community. Here we strive to outline a roadmap to achieving this elusive goal, examining competing architectures and technologies, and paving the way forward for the first experimental demonstration of post-classical computation. We firstly develop a practical model to compare the performance of boson-samplers and classical simulators. In this model, we find that low-photon-number boson-sampling operating in the current experimental regime (\mbox{$n<10$} photons) could beat present commodity computers with GHz clock-rates only if the overall system efficiency and repetition rate are sufficiently high. Further, we calculate the required efficiency and photon-number to surpass classical computers of different clock-rates using various experimental schemes. Especially, we find that only if both photon-number-resolving detectors and high-speed optical shutters are available, scattershot boson-sampling is feasibly scalable to tens of photons. In order to provide a clear roadmap for boson-sampling, we also review and discuss various state-of-the-art technologies for single-photon sources, quantum circuits, and single-photon detectors. We find that based on Moore's Law projections for the future development of classical supercomputing, a boson-sampler with $\sim 24$ photons, operating under experimentally plausible conditions, could outperform the top supercomputer 5 years into the future by an order of magnitude. We use this as a benchmark for heralding the onset of the post-classical era.
\end{abstract}

@@

In Sec.~\ref{sec:sampling_time}, taking the repetition rate of the sampling system into account, we develop a rigorous and fair model for comparing the performance of boson-samplers and classical simulators. Given a certain classical computer, the regime of quantum supremacy of boson-sampling is specified by a simple continuous curve in the plane of total efficiencies versus photon-number. To our surprise, there is such a (optimal) turning point in this curve where four-photon boson-samplers with repetition rates of 76MHz could beat present commodity computers with GHz clock-rates. \comment{There's a contradiction here. 1) we say that four photons can beat GHZ classical computer. 2) We say we need 20-30 photons to beat the computer. I don't follow.}. Based upon this, such a computer could only be defeated by \mbox{$20\sim 30$}-photon boson-sampling \cite{bib:2, bib:3}.

In Sec.~\ref{sec:exp_schemes}, we calculate the required efficiencies and photon-numbers for different experimental schemes to outperform classical computers of given clock-rates. In particular, we find that both photon-number-resolving detectors and high-speed optical shutters are indispensable to correctly implementing scattershot boson-sampling with tens of photons.

In Sec.~\ref{sec:fidelity_of_devices} we consider the implications of the fidelities of single-photon sources. This encompasses effects such as mode-mismatch and time-jitter. We describe the relationship between single-photon input fidelities and the confidence that a given sample taken from the output distribution correctly belongs to a legitimate boson-sampling distribution.

An intact boson-sampler includes three parts (see Fig.~\ref{fig:model}): single-photon sources, passive linear optical circuits, and single-photon detectors. A number of small-scale boson-sampling implementations have been reported in optical waveguides \cite{bib:4, bib:5, bib:6, bib:7, bib:8, bib:9} and fibre beamsplitters \cite{bib:10} using spontaneous parametric down-conversion (SPDC) sources, and fibre-loops \cite{bib:11} with quantum dot (QD) sources.

In Sec.~\ref{sec:adv_sources}, we introduce some of the most promising single-photon sources and their recent advances, including SPDC, four-wave mixing (FWM) and QDs.

In Sec.~\ref{sec:adv_networks}, we review and discuss some advances in linear optical networks, including optical waveguides, fibre-loops, and fibre beamsplitters.

In Sec.~\ref{sec:adv_detectors}, we consider single-photon detectors (SPD), including single-photon avalanche photodiodes (SPAD), superconducting nanowire single-photon detectors (SNSPD) and transition-edge sensors (TES). These three types of detectors represent the most mature, high-speed, and near-unit efficiency respectively.

Finally, and most importantly, in Sec.~\ref{sec:vision_for_the_future} we combine our analyses to construct a projection for what will be required to enter the post-classical era, which we define as outperforming the top supercomputer 5 years from now by an order of magnitude. We find that $\sim 24$-photon scattershot boson-sampling reaches this important threshold.

@@

How can a classical computer simulate this bosonic process, and sample from its exact or approximate probability distribution? A na{\"i}ve brute-force method is to calculate all $|\Phi|$ permanents of the set of submatrices $U_{S,T_i}$, thereby determining the full probability distribution, and then sample from this known distribution. Smarter classical algorithms exist to generate correct samples without knowing the entire underlying distribution. For example, using the acceptance-rejection method \cite{bib:fishman2013} one can sample an output configuration $\ket{T_i}$ uniformly from the configuration space and a number $u$ from the uniform distribution over $\{0,1\}$, then calculate the permanents of the respective submatrices and compare them to $u$; If \mbox{$u<|\mathrm{Per}(U_{S,T_i})|^2$}, we accept the sample $\ket{T_i}$; If not, it is rejected, and we repeat. Such methods could be successful with probability $O(1)$. One sample only requires calculating one permanent, significantly better than the brute-force method of calculating the entire distribution.

@@

As described above, the circuit itself consumes time resources $m^2\tau$, thus the effective repetition rate is,
\begin{align}
\frac{1}{m^2\tau}=\frac{R'}{m^2},
\end{align}
where $R'$ is the repetition frequency of the photonic time-bins, which we use instead of $R$ in Eq.~\ref{eq:tau_q} to obtain,
\begin{align}
\tau_t = \frac{m^2}{\eta^n R'}.
\end{align}
Again using \mbox{$\tau_t=\tau_c$} as the border between quantum/classical supremacy, we plot the critical photon-number to reach quantum supremacy as a function of $\eta$ for the time-bin encoding scheme.

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{curves_2}
\caption{The quantum and classical supremacy of (a) temporal-encoding, and (b) hybrid-encoding boson-sampling, is divided by the red line, where quantum supremacy is in the top-right region, and vice versa. The numbers 3, 6, etc. in the line refer to $10^3$FLOPS, $10^6$FLOPS etc. of classical computers respectively. The efficiency denoted on the horizontal axis is the overall system efficiency. Given the magnitude of the coupling strength, a single step including a beam splitter operation and phase-shifting operation takes \mbox{$\tau\sim0.3\mu\mathrm{s}$} \cite{bib:20}. Effective repeat frequency (a) \mbox{$R'=1/(13\mathrm{ns}\cdot 10^4)$}, (b) \mbox{$R'=1/(0.3\mu\mathrm{s}\cdot n^2).$}} \label{fig:curves_2}
\end{figure}

@@

Compared to fabricating a unitary network in waveguides, the spatial degree of freedom in the transverse axis is retained as there are $m$ storage resonators and auxiliary qubits in microwave boson-sampling. But the longitudinal spatial modes are replaced by $m$ controlled temporal steps. Suppose a single step including a beamsplitter operation and phase-shift operation takes time $\tau_m$, so the total operational time for an \mbox{$m\times m$} unitary transformation is $\tau_m m$. Taking the reciprocal of the total operational time as the effective repeat frequency, we obtain the formula for $\tau_q$ for this scheme. Comparing with $\tau_c$, we plot the supremacy boundary for microwave boson-sampling, shown in Fig.~\ref{fig:curves_2}(b).

From the perspective of the encoding scheme, the sampling speed (unitary transformation) of the microwave boson-sampler is much slower than that of spatially-encoding boson-samplers. As shown in Fig.~\ref{fig:curves_2}, to beat the same advanced classical computer, we actually need higher system efficiency or a larger number of photons if the microwave scheme is utilised. However, the advantage of the superconducting platform exactly lies in its marvelously high fidelities ($>0.90$) of generation and measurement processes \cite{bib:21}, to which no ordinary optical boson-sampler is comparable. Though with high processing speed, the effective repeat frequency of a spatially-encoded optical boson-sampler is greatly reduced by post-selection due to the limited collection and detection efficiency.

@@

Recently, Aaronson and Brod \cite{bib:33} demonstrated that if $O(1)$ photons are lost at the input (i.e. $k$ out of \mbox{$n+k$}), the probability of each output configuration is given by,
\begin{align}
\mathrm{Pr}(T) = \frac{1}{|\Lambda_{n+k,n}|} \sum_{s\in m,n+k,n} |\mathrm{Per}(U_{S,T})|^2,
\end{align}
where $\Lambda_{n+k,n}$ denotes the set of all collision-free basis states of $n$ photons of the input \mbox{$n+k$} photons, and \mbox{$|\Lambda_{n+k,n}| = \binom{n+k}{n}$}.

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{curves_loss}
\caption{The quantum and classical supremacy of boson-sampling with lost photons is separated by the red line, where the top-right side corresponds to the quantum regime and vice versa. Here the clock speed of the classical computer is gigaFLOPS, i.e $10^9$FLOPS. The efficiency denoted on the horizontal axis is the overall system efficiency. The numbers 0, 1, 2 \emph{etc.} in the line refer to the number of lost photons, $n_\mathrm{lost}$. The detection efficiency: (a) \mbox{$\eta_d=0.5$} (b) \mbox{$\eta_d=1$}.} \label{fig:curve_hybrid}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.5\columnwidth]{curve_scattershot}
\caption{The quantum and classical supremacy of scattershot boson-sampling is separated by the red line, where the top-right region belongs to quantum supremacy and vice versa. The numbers 3, 6, etc. on the lines refer to $10^3$FLOPS, $10^6$FLOPS etc. of classical computers respectively. The efficiency denoted on the horizontal axis is the single-photon efficiency, not including the preparation efficiency of the source, whereby the preparation efficiency of $n$ sources is substituted with $1/\sqrt{2\pi n}$ \cite{bib:36}.} \label{fig:curve_scattershot}
\end{figure}

@@

When the detectors are perfect but non-number-resolving, the probability that $n$ heralding detectors are triggered, and all of them result from single-photon pairs generated by $n$ SPDCs (ignoring higher order terms) is,
\begin{align}
p_\mathrm{input-correct} = \binom{m}{n} p^n(1-p-p^2)^{m-n}.
\end{align}
The total probability that $n$ SPDC sources generate photons is given by
\begin{align}
p_\mathrm{input-total} = \sum_{i=0}^n \binom{m}{n-i,i}p^{n+i}(1-p-p^2)^{m-n}.
\end{align}
Nevertheless, we cannot distinguish the correct preparation of $n$ single photons from the total occasions of $n$ heralded sources. As shown in Fig.~\ref{fig:SBS_pair_gen}, the correct generation ratio, defined as $p_\mathrm{input-correct}/p_\mathrm{input-total}$, decreases rapidly with increasing $n$.

@@

In SPDC, a laser pumps a second-order nonlinear material (e.g. BBO, KDP) and creates two parametric single photons (the signal and the idler) under the constraints of energy conservation and momentum conservation (also called phase matching):
\begin{align}
\omega_p &= \omega_s + \omega_i, \nonumber \\
k_p &=  k_s + k_i,
\end{align}
where $\omega$ is a photon's frequency, and $k$ its wave-vector, and $p$, $s$ and $i$ denote the pump, signal and idler, respectively.

There are several different types of phase matching:
\begin{itemize}
\item Type-I: The signal and the idler share the same polarization.
\item Type-II: The signal and the idler have orthogonal polarization.
\item Type-0: The pump, the signal and the idler share the same polarization.
\end{itemize}

In a nonlinear crystal, there is phase mismatch due to dispersion, but which can be compensated by using birefringence. The birefringence phase matching (BPM) requires at least one of two parametric photons to be extraordinary, resulting in spatial walk-off between the two photons. As the pump propagates through the crystal, the walk-off leads to a decrease in the beam overlap, thus limiting the effective length of the crystal. Additionally, there is a so-called quasi-phase matching (QPM), which compensates the phase mismatch by periodical inversion of the crystal’s nonlinear coefficient. QPM allows for collinear interaction among the pump, the signal and the idler. This avoids spatial walk-off and permits the usage of longer crystals and efficient collection of parametric photons. As a result, the best collection efficiency of ~90\% has been realized with quasi-phase-matching (QPM) \cite{bib:41, bib:42}.

@@

The problem of exaggerated physical size  also haunts another popular platform in the field of optical quantum information processing -- fused silica waveguides, fabricated using femtosecond laser direct-written (FLDW) technology. Unlike PLC fabrication, the FLDW is a powerful and flexible technique for rapid 3D fabrication, requiring no masking procedure or cleanroom environment. However, this one-step fabrication process also makes the propagation loss rely heavily on the motion control accuracy of the precision stage \cite{bib:63}. FLDW waveguides exhibit lowest losses on the order of 0.1dB/cm \cite{bib:63}, substantially higher than that of PLC waveguides. Also, the maximum refractive index contrast achieved so far is 1\%, which limits waveguide bends to a radius of about 15mm (see Tab.~\ref{tab:one}).

@@

\section{A vision for the future -- the post-classical era} \label{sec:vision_for_the_future}

@@

In our model, we can easily determine how many single-photons, and what repeat frequency and efficiency are needed to beat classical computers with given clock-speeds. To attain quantum supremacy, there are lower single-photon number thresholds ($<20$ photons) in systems with higher efficiencies and repeat frequencies. Therefore, improving repeat frequency plays a bigger role than photon number for those circuits with limited size but high transmittance, e.g., bulk optical circuits.
